Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-09-21 ms.tex
added a plot to show H-alpha line w/ Subaru."

\added{
\section{Stellar Activity}\label{sec:activity}
Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V. Rackham, private communication, 2018}
The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
}

>>>>

\added{
\section{Stellar Activity}\label{sec:activity}

The high resolution spectrum of \shStar\ allows us to measure the H$\alpha$ line, which is an indicator of stellar activity.
Figure \ref{fig:Halpha}, shows the Subaru HDS spectrum for

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{h_alpha_subaru.pdf}
\caption{H$\alpha$ line as measured by Subaru HDS on two adjacent nights in 2015.
The line's core changes noticeably between the two nights.}\label{fig:Halpha}
\end{centering}
\end{figure*}

Recently, \citet{rackham2018transitSourceEffect} have studied the effect of un-occulted spots on the transit depths of exoplanets orbiting M stars, the so-called transit source light effect.
For the observed amplitude variations of 0.8\% \citep{kawahara2013starspots}, scaling relations for K4 V dwarfs indicate that transit depths of exoplanets can be biased by 10$^{+20}_{-5}$\% depending on the distribution and sizes of spots if the transit chord is completely devoid of spots.\footnote{Benjamin V. Rackham, private communication, 2018}
The large physical size of \sha\, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and diminish the transit source effect, so \sha's 30\% transit depth variation would require a worst-case starspot coverage to be explained by un-occulted spots.
}
